---
name: Karthik Thrikkadeeri
qualifications: MSc
position: "Research Assistant"
address: "Nature Conservation Foundation, India"
profilepic: cvpic.jpg
www: kartrick.rbind.io
phone: +91 8129116328
email: "rikudoukarthik@gmail.com"
github: rikudoukarthik
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 3F6826
output: vitae::awesomecv
output_format: pdf_document
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(glue)
```

\hspace{1cm}
\hspace{1cm}

I am an ecologist interested in community ecology, migration and biogeography, with a focus on birds. My current work involves using large-scale citizen science data on bird occurrence to answer ecological questions. Beyond profession, birding occupies a prominent role in my life and is much more than a hobby.

# Personal Information

\begin{tabbing}

\textsc{Date of Birth} \hspace{0.5cm} \= 24 March 1999 \\
\textsc{Sex} \> Male (he/him) \\
\textsc{Nationality} \> Indian \\
\textsc{Marital Status} \> Unmarried \\
\textsc{Driving Licence} \> LMV \& MCWG (India) \\
\textsc{Languages} \> English, Malayalam (native), Hindi \\
\textsc{Interests} \> Ecological research (community ecology, migration, biogeography) \\
\> Data visualisation, poetry, birdwatching \href{https://ebird.org/profile/ODQxNTky}{(eBird profile)} \\

\end{tabbing}

# Education

```{r}
library(tibble)
tribble(~ Degree, ~ Year, ~ Institution, ~ Where, ~Details, 
  "MSc in Ecology", "2019--21", "University of South Bohemia", "Ceske Budejovice, Czech Republic", "Thesis: \"Habitat selection in post-breeding temperate forest birds\"",
  "MSc in Ecology", "2019--21", "University of South Bohemia", "Ceske Budejovice, Czech Republic", "Supervisor: Katerina Sam",
  "BSc in Biotechnology, Chemistry, Zoology", "2016--19", "CHRIST (Deemed to be University)", "Bangalore, Karnataka, India", NA) %>% 
  detailed_entries(Degree, Year, Institution, Where, Details)
```


# Skills

\begin{tabbing}

\textsc{Fieldwork} \hspace{0.5cm} \= Experience with bird research, butterfly and odonate surveys, vegetation sampling \\
\textsc{Software} \> R, R Markdown, MS Office, Git/GitHub, ImageJ, Adobe Illustrator, Adobe Lightroom \\

\end{tabbing}

# Experience

I have been birding for more than six years now, and the obsession has only been getting stronger. I have been fortunate enough to experience the birds, habitats and landscapes of three continents in the Old World, and this I believe has been an invaluable asset. I am currently an eBird Hotspot Editor for the states of Tripura and Meghalaya ([my eBird profile](https://ebird.org/profile/ODQxNTky)). I enjoy birding by ear and like to record and study bird vocalisations while birding.

During my time as a master’s student in Czechia, I was part of the small but growing community of eBirders in the country, and thereby helped “survey” the region by seeding hotspots and feeding checklist data into eBird. I also lived in my university campus and therefore was able to build a comprehensive checklist of campus birds ([campus hotspot](https://ebird.org/hotspot/L9974526)). I was a prolific birder in my bachelor’s university campus as well ([hotspot](https://ebird.org/hotspot/L3349006)).

I have participated in several bird surveys in India, in places like Silent Valley (KL), Panna (MP), Attappady (KL), Periyar (KL), Betul (MP), etc. I have helped conduct bird monitoring workshops in northeast India, and I recently also helped organise a bird survey in Wayanad (North) Forest Division (KL; [survey report](https://ebird.org/tripreport/111831)).
