---
author:
  firstname: Karthik
  lastname: Thrikkadeeri
  position: "PhD Student, Montaño Lab"
  address: "Louisiana State University, Baton Rouge, USA"
  contacts:
    - icon: fa envelope
      text: "rikudoukarthik@gmail.com"
      url: "mailto:rikudoukarthik@gmail.com"
    - icon: assets/icon/bi-house-fill.svg
      text: kartrick.com
      url: https://kartrick.com
    - icon: fa brands github
      text: GitHub
      url: https://github.com/rikudoukarthik
    - icon: fa brands orcid
      text: ORCiD
      url: https://orcid.org/0000-0003-2863-5879
    # - icon: fa brands linkedin
    #   text: LinkedIn
    #   url: https://linkedin.com/in/example
    - icon: assets/icon/si-bluesky.svg # fa brands bluesky not working
      text: Bluesky
      url: https://bsky.app/profile/kartrick.bsky.social
# profile-photo: "cvpic.jpg"
style:
   color-accent: "A92330"
   color-accent-dark: "771822"
   font-text: "Libertinus Serif"
   font-header: "Petrona"
   # for original Font Awesome font, see https://github.com/kazuyanagimoto/cv/tree/d7118a5d6317f3758447a8a9054a8577f42bc30a/assets/fonts/fontawesome
format: awesomecv-typst
# install.packages("typstcv", repos = "https://kazuyanagimoto.r-universe.dev")
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
# library(vitae)
library(tidyverse)
library(glue)
# library(rorcid)
library(lubridate)
library(typstcv)
```

# Personal Information

**Date of Birth:** 24 March 1999  
**Sex:** Male (he/him)  
**Nationality:** Indian  
**Driving Licence:** LMV & MCWG (India), Class E (USA)  
**Languages:** English, Malayalam (native), Hindi  

### Interests

- Ecological research (community ecology, macroecology, biogeography)
- Data analysis and visualisation ([fun data projects](https://kartrick.com/sandbox/))
- Birdwatching ([eBird profile](https://ebird.org/profile/ODQxNTky))
- Poetry and creative non-fiction writing
- Hip-hop

# Education

### Degrees

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, ~detail1, ~detail2,
  
  "PhD, Biological Sciences (ongoing)", "Baton Rouge, US", "2025--present",
  "Louisiana State University", 
  # "Thesis: XYZ"
  "Division: Systematics, Ecology and Evolution",
  "Supervisor: Flavia Montaño-Centellas",
  
  "MSc, Ecology", "České Budějovice, CZ", "2019--21",
  "University of South Bohemia", 
  "Thesis: Habitat selection in post-breeding temperate forest birds",
  "Supervisor: Kateřina Sam",
  
) %>% 
  resume_entry(details = grep("^detail", names(.)))

```

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, 
  
  "BSc, Biotechnology, Chemistry, Zoology", "Bengaluru, IN", "2016--19",
  "Christ University"
  
) %>% 
  resume_entry()

```

### Courses/workshops

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, ~details,
  
  "Introduction to Remote Sensing using QGIS", 
  "Bengaluru, IN", 
  "21--25 Nov 2022",
  "Azim Premji University",
  "Basic principles of remote sensing, characterising different features of land surface, generating maps with land cover statistics"
) %>% 
  resume_entry(details = "details")

```

# Certifications

```{r}
#| output: asis

tribble(
  ~title, ~date, ~description, ~details, 
  
  "English CEFR C2", 
  "2023",
  "IELTS (Academic)", 
  "Listening: 9.0; Reading: 9.0; Writing: 7.5; Speaking: 8.0; Overall Band Score: 8.5.",
  
  "All-India Topper, Ecology and Evolution (EY)", 
  "2023",
  "Graduate Aptitude Test in Engeering (GATE)", 
  "Marks: 84.33; Score: 1000.",

  "English CEFR C2", 
  "2018",
  "IELTS (Academic)", 
  "Listening: 9.0; Reading: 9.0; Writing: 7.0; Speaking: 8.0; Overall Band Score: 8.5."
  
) %>% 
  resume_entry(details = "details")

```

# Awards

```{r}
#| output: asis

data.frame(
  title = "Rector's Award",
  location = "České Budějovice, CZ",
  date =  "2021",
  description = "University of South Bohemia, 25 May 2021",
  details = "CZK 2,500 (\\~€100), for outstanding results in study"
) %>% 
  resume_entry(details = "details")

```

```{r}
#| output: asis

data.frame(
  title = "Graduate study Merit Scholarship",
  location = "České Budějovice, CZ",
  date =  "2020",
  description = "University of South Bohemia, Oct 2020--May 2021",
  details1 = "CZK 1,500 (\\~€60) awarded per month for 10 months in second year of study",
  details2 = "Scholarship of the Ministry of Education, Youth and Sports"
) %>% 
  resume_entry(details = grep("^detail", names(.)))

```

# Publications

### Research articles

<!-- This can be selected publications, so manually enter. Particularly since space is limited and need to highlight my name. -->

1. A Viswanathan, **K Thrikkadeeri**, et al. (2025). State of India’s Birds 2023: A framework to leverage semi-structured citizen science for bird conservation. *Ecosphere* 16(7). DOI: https://doi.org/10.1002/ecs2.70290
1. **K Thrikkadeeri** & A Viswanathan (2024). Despite short-lived changes, COVID-19 pandemic had minimal large-scale impact on citizen science participation in India. *Ornithological Applications* 126(4). DOI: https://doi.org/10.1093/ornithapp/duae024 
1. **K Thrikkadeeri**, ..., A Viswanathan (2024). Birdwatchers piecing together Locustella jigsaw: Insights on the wintering distribution of the cryptic West Himalayan Bush Warbler *Locustella kashmirensis*. *Indian BIRDS* 20(3). 
1. L Schillé, ..., **K Thrikkadeeri**, et al. (2024). Latitudinal gradient in avian insectivory: complementary effects of climate, habitat and bird diversity. *Journal of Biogeography* 51(6). DOI: https://doi.org/10.1111/jbi.14808 
1. J Praveen, ..., **K Thrikkadeeri**, et al. (2022). Kerala Bird Atlas 2015--20: features, outcomes and implications of a citizen-science project. *Current Science* 122(3). 

### Software

1. **K Thrikkadeeri** (2024). *skimmr: Working with eBird data made easy*. R package version 0.0.0.9005. URL: https://rikudoukarthik.github.io/skimmr/

### Reports

1. **SoIB** (2023). *State of India's Birds, 2023: Range, trends, and conservation status*. The SoIB Partnership. Pp. 119. DOI: https://doi.org/10.5281/zenodo.11124590 

### Books 

1. PU Antony, ..., **K Thrikkadeeri**, et al. (2018). *Butterflies of Christ University Main Campus---A Pictorial Guide*. Centre for Publications, Christ University, Bangalore, India. 

### In pipeline

1. **K Thrikkadeeri** and A Viswanathan *(in prep.)*. No evidence at large scale for “return” of bird life in the Indian anthropause.
1. **K Thrikkadeeri**, I Freiberga, LR Jorge, K Sam *(in prep.)*. Post-breeding birds dynamically track habitat structure over the season in a Central European forest.
1. **K Thrikkadeeri**, ..., G Shahabuddin *(in prep.)*. A checklist of butterflies from a land-use intensification gradient in Kumaon Himalayas.



# Skills

### Field

- Point counts, line transects, all-out/opportunistic search
- Sound recording (birds), telephoto photography (birds), macro photography
- Camera trapping, PCQ vegetation sampling, radio telemetry 
- Excellent sight and sound ID of birds (India, Europe)
- Extensive field experience in diverse and challenging landscapes, habitats and terrains

### Technical

- Quantitative ecology and research design
- Data curation, management, processing and wrangling
- Reproducibility, version control and transparency in research workflows
- Copy editing and proofreading (English)

### Software

- R, R/Quarto Markdown & allies, Git/GitHub, QGIS
- ChatGPT, Bard
- Audacity, MS Office, Google Suite, Canva, ImageJ 

### Personal qualities

- Ambitious, patient, persistent, self-motivated, time management skills

# Work Experience

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, 
  
  "Louisiana State University", 
  "Baton Rouge, US", 
  "Jan 2025--present",
  "Graduate Assistant"
  
) %>% 
  resume_entry()

```

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, 
  ~detail1, ~detail2, ~detail3, ~detail4, ~detail5, ~detail6, ~detail7,
  
  "Nature Conservation Foundation", 
  "Bengaluru, IN", 
  "Apr 2023--Dec 2024",
  "Senior Research Assistant", 
  
  "SoIB 2023: Contributed to analysis, visualisation and writing for two chapters (large-scale trends, systematic monitoring) of report, and also produced website-specific outputs",
  "SoIB 2023: Unified various analyses into pipeline framework, and functionised/parametrised scripts and added annotations, to improve accessibility to team as well as others",
  "SoIB 2023: Cleaned, structured and organised GitHub repository to archive",
  "SoIB 2023: Contributed to editing and proofreading as well as bibliography management for the full report", 
  "Created an R package 'skimmr' for functions used repeatedly when working with eBird data in R in the Indian context",
  "Created a Shiny app based on eBird API that allows the user to generate a summary of the eBirding that happened in a given administrative unit on a given date(s)",
  "Created a GitHub repository to collate mapping data useful for eBird data analysis in the Indian context---mostly contains open shapefiles of administrative units",
  
  "Nature Conservation Foundation", 
  "Bengaluru, IN", 
  "Aug 2021--Mar 2023",
  "Research Assistant", 
  
  "Analysed the effect of the COVID-19 pandemic on birdwatching and eBird data in India, and its implications for research using this data; wrote up and submitted manuscript to a peer-reviewed journal",
  "Established a version control (Git/GitHub) workflow for Bird Count India analyses to enable reproducibility as well as transparency",
  "Created a periodic analysis framework to identify and track regions in India that are most underrepresented in eBird data, in order to identify regions of priority where concerted action (strategised from these metrics) is required",
  "Created eBirding point maps for the country as well as for each state in India, made easily accessible to users and updated monthly", 
  "Automated several periodically occurring data analysis tasks of Bird Count India (tracking metrics, results of challenges & birding events [post-hoc from EBD and also live summaries using eBird API and R], etc.)",
  "Improved eBird data quality in India by creating updated and more fine-scale (district-wise) filters for Tripura state",
  "Assisted birders with their queries regarding eBird data and how to analyse it for their own studies",
  
  "Biology Centre of the Czech Academy of Sciences", 
  "České Budějovice, CZ", 
  "Dec 2020--Feb 2021",
  "Part-time Employee", 
  "Collated Kateřina Sam's Papua New Guinea bird datasets spanning c. 4 years and uploaded to eBird",
  NA_character_, NA_character_, NA_character_, NA_character_, NA_character_, NA_character_,  
  
  "Biology Centre of the Czech Academy of Sciences", 
  "České Budějovice, CZ", 
  "Oct 2020",
  "Part-time Employee", 
  "Calculated herbivory damage from images of collected leaves from Cameroon using ImageJ",
  NA_character_, NA_character_, NA_character_, NA_character_, NA_character_, NA_character_,  
  
  "Centre for Ecology Development and Research (CEDAR Himalaya)", 
  "Kumaon, IN", 
  "Apr 2018--May 2018",
  "Research intern", 
  "Studied butterfly diversity patterns across a land-use intensification gradient in oak-pine forests of Kumaon Himalayas",
  NA_character_, NA_character_, NA_character_, NA_character_, NA_character_, NA_character_,  
  
  "Agumbe Rainforest Research Station (ARRS)", 
  "Agumbe, IN", 
  "Apr 2017--May 2017",
  "Research volunteer", 
  "Assisted in field work and data entry for a project on breeding ecology of the Yellow-wattled Lapwing",
  "Additionally, learned basics of camera trapping, scale counting for snakes and PCQ vegetation survey", 
  NA_character_, NA_character_, NA_character_, NA_character_, NA_character_,  
  
  
  
) %>% 
  resume_entry(details = grep("^detail", names(.)))

```

# Teaching

### Courses

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, 
  
  # "BIOL 1209 Introductory Biology Lab II", 
  # "Baton Rouge, US", 
  # "Aug 2025--present",
  # "Louisiana State University",
  # 
  "BIOL 1208 Introductory Biology Lab I", 
  "Baton Rouge, US", 
  "Jan 2025--May 2025",
  "Louisiana State University",
  
) %>% 
  resume_entry()

```

### Workshops

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, 
  ~detail1, ~detail2, ~detail3,
  
  "Using R for analyses using eBird data: An introduction", 
  "Thrissur, IN", 
  "Jun 2024",
  "Kerala Bird Monitoring Meet (KBMM) 2024", 
  "Led c. 3 h crash course for c. 20 participants (birders) with assistance from Praveen J", 
  NA_character_, NA_character_, 
  
  "Analysing eBird data with R", 
  "Thrissur, IN", 
  "Jun 2023",
  "Kerala Bird Monitoring Meet (KBMM) 2023", 
  "Led workshop for c. 20 participants (birders) with assistance from Praveen J", 
  NA_character_, NA_character_, 
  
  "Introduction to Merlin and eBird tools", 
  "Silchar, IN", 
  "May 2022",
  "Assam University, Silchar", 
  "Assisted Mittal Gala in short outdoor training session for 8 MSc Physics students", 
  "Introduced features of Merlin Bird ID and eBird Mobile, and demonstrated practical usage", 
  "Interacted with students on general queries about birds and birding", 
  
  "Bird monitoring and eBird", 
  "Lembucherra, IN", 
  "May 2022",
  "College of Agriculture, Lembucherra", 
  "Assisted Mittal Gala in indoor workshop for c. 40 participants (students and local birders)", 
  "Provided technical assistance, coordination support, and ad-hoc engagement with audience", 
  NA_character_, 
  
) %>% 
  resume_entry(details = grep("^detail", names(.)))

```

# Presentations

<!-- ### Contributed -->

**2023:** *Citizen Science at NCF Field Sites*. Presented with Mittal Gala. NCF Annual Meet 2023, Mysuru, IN.

**2022:** *The impact of the COVID-19 pandemic on birding and birds in India*. NCF Annual Meet 2022, Mysuru, IN. ([Click for slides or code](https://kartrick.com/slides/2022_ncf-am_covid-ebirding/))

**2022:** *The impact of the COVID-19 pandemic on birding and birds in India*. International Ornithological Congress 2022, online. ([Click for slides or code](https://kartrick.com/slides/2022_ioc-covid-ebirding/))

**2022:** *The impact of the COVID-19 pandemic on bird monitoring in India* (poster). Bird Monitoring Symposium 2022, online.

**2019:** *Inventory of butterfly species along a land-use intensification gradient in moist temperate forest biome in Kumaon Himalayas*. Ecology Seminar, University of South Bohemia, CZ.

**2018:** *A study on avian diversity in an industrial area of the Palghat Gap*. National Seminar on Development and Ecological Sustainability: Issues in Emerging India (DESIEI) 2018, Bengaluru, IN.

<!-- ### Public -->

# Field Activities

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, 
  ~detail1, ~detail2, ~detail3, ~detail4,
  
  "Bird Surveys", 
  "IN", 
  "2019--24",
  "Volunteer data collector", 
  "Periyar Bird Survey (Jan 2023) in Periyar Tiger Reserve, Kerala (team lead)",
  "Attappady Bird Survey (Dec 2022) in Attappady, Kerala (team lead)",
  "Panna Bird Survey (Mar 2022) in Panna Tiger Reserve, Madhya Pradesh (team lead)",
  "Wet Season Survey of Kerala Bird Atlas (Jul 2019) in Silent Valley National Park, Kerala",
  
  "Field research", 
  "Dudhwa, IN", 
  "Apr 2023",
  "Team member", 
  "Contributed to data collection and discussions during the Bengal Florican survey (part of the grassland monitoring project of The Habitats Trust) in Dudhwa--Pilibhit landscape, Uttar Pradesh", 
  NA_character_, NA_character_, NA_character_,
  
  "Expeditions", 
  "Betul, IN", 
  "Feb 2023",
  "Expedition member", 
  "Joined mini-expedition to survey the birds of Betul, an underbirded district in Madhya Pradesh", 
  NA_character_, NA_character_, NA_character_,

) %>% 
  resume_entry(details = grep("^detail", names(.)))

```

# Other Activities

### Organisational

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, 
  ~detail1, ~detail2, 
  
  "North Wayanad Forest Division Bird Survey 2023", 
  "North Wayanad, IN", 
  "Mar 2023",
  "Organiser", 
  "Helped formulate survey methodology, and managed technical logistics (eBird as a tool) and data quality",
  NA_character_, 
  
  "National Seminar DESIEI 2018", 
  "Bengaluru, IN", 
  "Dec 2018",
  "Organiser, Editor", 
  "Member of symposium's Organising Committee",
  "Led editorial work including editing, proofreading, typesetting, and publishing of Abstracts book"

) %>% 
  resume_entry(details = grep("^detail", names(.)))

```

### Volunteering

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, ~details, 
  
  "eBird data analysis consultation, Bird Count India", 
  "Online", 
  "Dec 2022--Dec 2024",
  "Office Hours", 
  "Offered office hours consultation for individuals or groups on how to analyse eBird data (see more at https://birdcount.in/analysis-consultation/)",
  
  "eBird data quality", 
  "Online", 
  "May 2022--present",
  "Regional Reviewer & Hotspot Editor", 
  "Regional Reviewer for Tripura, IN; Hotspot Editor for Tripura, In & Meghalaya, IN",
  
  "Bird Monitoring Symposium 2023", 
  "Online", 
  "Mar 2023",
  "Volunteer", 
  "Managed session talks, Q&As and comments on Discord, as well as assisted participants with queries",
  
  "NCF Annual Meet 2022", 
  "Mysuru, IN", 
  "Oct 2022",
  "Volunteer", 
  "MCd a session of talks",
  
  "Bird Monitoring Symposium 2022", 
  "Online", 
  "Apr 2022",
  "Volunteer", 
  "Managed session talks, Q&As and comments on Slack, as well as assisted participants with queries",

) %>% 
  resume_entry(details = "details")

```

### Administrative

```{r}
#| output: asis

tribble(
  ~title, ~location, ~date, ~description, ~details, 
  
  "Server administration", 
  "Bengaluru, IN", 
  "2022--24",
  "Coordinator", 
  "Coordinated usage of NCF High Altitude Programme's high-performance server among various interested parties, as well as its maintenance",

) %>% 
  resume_entry(details = "details")

```

# Mentoring

- **Vyom Vyas:** Assisted in designing a behavioural study on the breeding ecology of Purple Sunbird

{{< pagebreak >}}

# Referees

**Dr Ashwin Viswanathan**

Research Associate, Education and Public Engagement  
Nature Conservation Foundation, Mysuru, India  
Email: ashwinv@ncf-india.org  

**Dr Suhel Quader**

Scientist, Education and Public Engagement  
Nature Conservation Foundation, Mysuru, India  
Email: suhelq@ncf-india.org  

**Praveen J**

Scientist, Education and Public Engagement  
Nature Conservation Foundation, Mysuru, India  
Email: praveen.j@ncf-india.org  

**Mgr Katerina Sam, PhD**

Head, Laboratory of Multitrophic Interactions  
Biology Centre of the Czech Academy of Sciences, České Budějovice, Czech Republic  
Email: katerinatvardikova@gmail.com  

**Dr PU Antony**

Retired Professor, Department of Zoology  
Christ University, Bengaluru, India  
Email: antonypulahannan@gmail.com  
