---
name: Karthik Thrikkadeeri
qualifications: MSc
position: "Senior Research Assistant"
address: "Nature Conservation Foundation, India"
profilepic: cvpic.jpg
www: kartrick.rbind.io
phone: +91 8129116328
email: "rikudoukarthik@gmail.com"
github: rikudoukarthik
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 3F6826
output: vitae::awesomecv
output_format: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(glue)
```

\hspace{1cm}
\hspace{1cm}

# Personal Information

\begin{tabbing}

\textsc{Date of Birth} \hspace{0.5cm} \= 24 March 1999 \\
\textsc{Sex} \> Male (he/him) \\
\textsc{Nationality} \> Indian \\
\textsc{Marital Status} \> Unmarried \\
\textsc{Driving Licence} \> LMV \& MCWG (India) \\
\textsc{Languages} \> English, Malayalam (native), Hindi \\
\textsc{Interests} \> Ecological research (community ecology, migration, biogeography) \\
 \> Birdwatching \href{https://ebird.org/profile/ODQxNTky}{(eBird profile)} \\
 \> Poetry and creative non-fiction writing \\
 \> Data analysis and visualisation \\

\end{tabbing}

# Education

```{r}
library(tibble)
tribble(~ Degree, ~ Year, ~ Institution, ~ Where, ~Details, 
  "MSc in Ecology", "2019--21", "University of South Bohemia", "České Budějovice, Czech Republic", "Thesis: \"Habitat selection in post-breeding temperate forest birds\"",
  "MSc in Ecology", "2019--21", "University of South Bohemia", "České Budějovice, Czech Republic", "Supervisor: Kateřina Sam",
  "BSc in Biotechnology, Chemistry, Zoology", "2016--19", "CHRIST (Deemed to be University)", "Bangalore, Karnataka, India", NA) %>% 
  detailed_entries(Degree, Year, Institution, Where, Details)
```


# Skills

\begin{tabbing}

\textsc{Fieldwork} \hspace{0.5cm} \= Experience with bird research, butterfly and odonate surveys, vegetation sampling \\
\textsc{Software} \> R, R Markdown, Git/GitHub, MS Office, ImageJ \\

\end{tabbing}




# Experience

```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Senior Research Assistant", "Nature Conservation Foundation", "Bangalore, Karnataka, India", "Apr 2023--present", NA,
  "Research Assistant", "Nature Conservation Foundation", "Bangalore, Karnataka, India", "Aug 2021--Mar 2023", NA,
  "Field volunteer", "Panna Bird Survey 2022", "Panna, Madhya Pradesh, India", "Mar 2022", "Volunteered for first bird survey in Panna Tiger Reserve",
  "Part-time employee", "Biology Centre, Czech Academy of Sciences", "Ceske Budejovice, Czech Republic", "Dec 2020--Feb 2021", "Collation of Katerina Sam's Papua New Guinea bird datasets spanning ca. 4 years and uploading to eBird",
  "Part-time employee", "Biology Centre, Czech Academy of Sciences", "Ceske Budejovice, Czech Republic", "Oct 2020", "Calculated herbivory damage from images of collected leaves from Cameroon using ImageJ software",
  "Field volunteer", "Kerala Bird Atlas---Wet Season Survey 2019", "Palakkad, Kerala, India", "Jul 2019", "Assisted in monsoon bird survey in Silent Valley National Park",
  "Research intern", "Centre for Ecology Development and Research (CEDAR Himalaya)", "Kumaon, Uttarakhand, India", "Apr 2018--May 2018", "Studied butterfly diversity patterns across a land-use intensification gradient in oak-pine forests of Kumaon Himalayas",
  "Research volunteer", "Agumbe Rainforest Research Station (ARRS)", "Agumbe, Karnataka, India", "Apr 2017--May 2017", "Assisted in field work and data entry for a project on breeding ecology of the Yellow-wattled Lapwing",
  "Research volunteer", "Agumbe Rainforest Research Station (ARRS)", "Agumbe, Karnataka, India", "Apr 2017--May 2017", "Additionally, learned basics of camera trapping, scale counting for snakes and PCQ vegetation survey"
) %>% 
  detailed_entries(company, dates, role, loc, details)
```


# Presentations

## Conference Talks

\textbf{2019.} Inventory of butterfly species along a land-use intensification gradient in moist temperate forest biome in Kumaon Himalayas.
\textit{Ecology Seminar, University of South Bohemia, Czech Republic.} 

\textbf{2018.} A study on avian diversity in an industrial area of the Palghat Gap.
\textit{National Seminar on Development and Ecological Sustainability: Issues in Emerging India (DESIEI---2018), CHRIST (Deemed to be University), Bengaluru, India.}

# Publications

## Research articles

```{r publications} 

# bibliography_entries(file = "my_publications.bib", "Pubs")
scholar::get_publications("rGqtkNgAAAAJ") %>% 
  detailed_entries(what = author,
                   when = year,
                   with = title,
                   where = journal,
                   why = cites)

```

1. J Praveen, ..., **K Thrikkadeeri** et al. (2022). Kerala Bird Atlas 2015---20: features, outcomes and implications of a citizen-science project. *Current Science* 122(3). 
1. **K Thrikkadeeri**, R Chanda, RD Kishore and R Singh (under review). A photographic record of Jungle Cat *Felis chaus* from an urban hotspot in Bengaluru city, Karnataka, India.
1. **K Thrikkadeeri**, I Freiberga, LR Jorge, K Sam (in prep.). Habitat selection in post-breeding temperate forest birds.
1. **K Thrikkadeeri**, ..., G Shahabuddin (in prep.). A checklist of butterflies from a land-use intensification gradient in Kumaon Himalayas.
1. **K Thrikkadeeri** and A Viswanathan (in prep.). Birds in the time of COVID: Pandemic effects illuminated by birdwatchers, and implications for citizen science inference.

## Books 

1. PU Antony, ..., **K Thrikkadeeri** et al. (2018). Butterflies of Christ University Main Campus---A Pictorial Guide. *Centre for Publications, Christ University, Bangalore, India*. 

# Memberships

```{r}

tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Volunteer", "Forest Watch", "Wayanad, Kerala, India", "2019--present", NA,
  "MSc Student", "Laboratory of Multitrophic Interactions", "České Budějovice, Czech Republic", "2019--2021", NA, 
  "Editorial Board", "Organising Committee, National Seminar DESIEI---2018", "Bangalore, Karnataka, India", "2018", "Majorly involved in all editorial work including editing, proofreading, typesetting and publishing of Abstracts book",
  "Student Volunteer", "Green Army, Christ University", "Bangalore, Karnataka, India", "2016--19", "A student-based forum for wildlife and conservation",
    "Student Volunteer", "Green Army, Christ University", "Bangalore, Karnataka, India", "2016--19", "Organised and took part in multiple nature camps and day-treks",
    "Student Volunteer", "Green Army, Christ University", "Bangalore, Karnataka, India", "2016--19", "Helped organise national seminars and conducted several awareness programmes like wildlife-themed workshops",
    "Student Volunteer", "Green Army, Christ University", "Bangalore, Karnataka, India", "2016--19", "Conducted tree counts and tree plantation drives",
    "Student Volunteer", "Green Army, Christ University", "Bangalore, Karnataka, India", "2016--19", "Worked for the rejuvenation of a dying lake in Bangalore city which included working with government authorities and acted as a liaison for the local communities"
) %>% 
  detailed_entries(role, dates, company, loc, details)

```


\newpage

# Referees

## Mgr. Katerina Sam, Ph.D.
Head, Laboratory of Multitrophic Interactions \newline
Biology Centre of Czech Republic, Ceske Budejovice, Czech Republic \newline
Email: katerinatvardikova@gmail.com \newline
Phone no.: +420 776 823 074

## Dr. Antony PU
Retired Professor, Department of Zoology \newline
CHRIST (Deemed to be University), Bangalore, Karnataka, India \newline
Email: antony.pu@christuniversity.in \newline
Phone no.: +91 9886887131, +91 8310082860