---
name: Karthik Thrikkadeeri
qualifications: MSc
position: "Senior Research Assistant"
address: "Nature Conservation Foundation, India"
profilepic: cvpic.jpg
www: kartrick.rbind.io
phone: +91 8129116328
email: "rikudoukarthik@gmail.com"
github: rikudoukarthik
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: A92330
header-includes:
  - \definecolor{linkscolor}{HTML}{66151D}
  - \hypersetup{colorlinks=true, urlcolor=linkscolor}
output: vitae::awesomecv
output_format: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(glue)
library(rorcid)
library(lubridate)
```

\hspace{1cm}
\hspace{1cm}

# Personal Information

\begin{tabbing}

\textsc{Date of Birth} \hspace{0.5cm} \= 24 March 1999 \\
\textsc{Sex} \> Male (he/him) \\
\textsc{Nationality} \> Indian \\
\textsc{Marital Status} \> Unmarried \\
\textsc{Driving Licence} \> LMV \& MCWG (India) \\
\textsc{Languages} \> English, Malayalam (native), Hindi \\
\textsc{Interests} \> Ecological research (community ecology, migration, biogeography) \\
 \> Birdwatching \href{https://ebird.org/profile/ODQxNTky}{(eBird profile)} \\
 \> Poetry and creative non-fiction writing \\
 \> Quantitative data analysis and visualisation \href{https://kartrick.rbind.io/kartrix/}{(fun data projects)} \\

\end{tabbing}

# Education

## Degrees

```{r}
orcid_educations("0000-0003-2863-5879") %>% 
  pluck("0000-0003-2863-5879", "affiliation-group", "summaries") %>% 
  bind_rows() %>% 
  # adding details to any item
  group_by(pick(everything())) %>% 
  reframe(details = case_when(
    
    `education-summary.role-title` == "MSc in Ecology" ~ c(
      "Thesis: \"Habitat selection in post-breeding temperate forest birds\"",
      "Supervisor: Kateřina Sam"
    ),
    TRUE ~ NA
    
  )) %>% 
  distinct() %>% 
  detailed_entries(what = `education-summary.role-title`,
                   when = glue("{`education-summary.start-date.year.value`}--{`education-summary.end-date.year.value`}"),
                   with = `education-summary.organization.name`,
                   where = glue("{`education-summary.organization.address.city`}, {`education-summary.organization.address.country`}"),
                   why = details)
```

## Courses/Workshops

```{r}
tribble(
  ~Name, ~Year, ~Institution, ~where, ~Details,
  "Introduction to Remote Sensing using QGIS", "21--25 Nov 2022", 
  "Azim Premji University", "Bengaluru, IN", 
  "Basic principles of remote sensing, characterising different features of land surface, generating maps with land cover statistics",
        ) %>% 
  detailed_entries(what = Name, 
                   when = Year,
                   with = Institution, 
                   where = where,
                   why = Details)
```

# Skills

\begin{tabbing}

\textsc{Fieldwork} \hspace{0.5cm} \= Experience with bird research, butterfly and odonate surveys, vegetation sampling \\
\textsc{Software} \> R, R Markdown, Git/GitHub, MS Office, ImageJ \\

\end{tabbing}

# Work Experience

```{r}
orcid_employments("0000-0003-2863-5879") %>% 
  pluck("0000-0003-2863-5879", "affiliation-group", "summaries") %>% 
  bind_rows() %>% 
  mutate(across(c("employment-summary.end-date.year.value", "employment-summary.end-date.month.value"),
                ~ case_when(is.na(.) ~ "present", TRUE ~ .))) %>% 
  mutate(start_date = glue("{month(as.numeric(`employment-summary.start-date.month.value`), label = TRUE)} {`employment-summary.start-date.year.value`}"),
         end_date = case_when(
           `employment-summary.end-date.year.value` == "present" ~ `employment-summary.end-date.year.value`,
           TRUE ~ glue("{month(as.numeric(`employment-summary.end-date.month.value`), label = TRUE)} {`employment-summary.end-date.year.value`}")
         )) %>% 
  # adding details to any item
  group_by(pick(everything())) %>% 
  reframe(details = case_when(
    
    `employment-summary.role-title` == "Part-time employee" & start_date == "Dec 2020" ~ 
      "Collated Kateřina Sam's Papua New Guinea bird datasets spanning c. 4 years and uploaded to eBird",
    
    `employment-summary.role-title` == "Part-time employee" & start_date == "Oct 2020" ~ 
      "Calculated herbivory damage from images of collected leaves from Cameroon using ImageJ software",
    
    `employment-summary.role-title` == "Research intern" & 
      str_detect(`employment-summary.organization.name`, "CEDAR") ~ 
      "Studied butterfly diversity patterns across a land-use intensification gradient in oak-pine forests of Kumaon Himalayas",
    
    `employment-summary.role-title` == "Research volunteer" & 
      str_detect(`employment-summary.organization.name`, "ARRS") ~ 
      c("Assisted in field work and data entry for a project on breeding ecology of the Yellow-wattled Lapwing",
        "Additionally, learned basics of camera trapping, scale counting for snakes and PCQ vegetation survey"),
    
    TRUE ~ NA
    
  )) %>% 
  distinct() %>% 
  arrange(desc(`employment-summary.start-date.year.value`),
          desc(`employment-summary.start-date.month.value`)) %>% 
  detailed_entries(what = `employment-summary.role-title`,
                   when = case_when(start_date != end_date ~ glue("{start_date}--{end_date}"),
                                    TRUE ~ start_date),
                   with = `employment-summary.organization.name`,
                   where = glue("{`employment-summary.organization.address.city`}, {`employment-summary.organization.address.country`}"),
                   why = details)
```

# Publications

## Research articles

<!-- This can be selected publications, so manually enter. Particularly since space is limited and need to highlight my name. -->

1. L Schillé, ..., **K Thrikkadeeri** et al. (2023). Latitudinal gradient in avian insectivory: complementary effects of climate, habitat and bird diversity. Preprint at *BioArxiv*: https://doi.org/10.1101/2023.01.19.524212.
1. J Praveen, ..., **K Thrikkadeeri** et al. (2022). Kerala Bird Atlas 2015---20: features, outcomes and implications of a citizen-science project. *Current Science* 122(3). 

## Reports

1. SoIB 2023. *State of India's Birds, 2023: Range, trends, and conservation status*. The SoIB Partnership. Pp. 119.

## Books 

1. PU Antony, ..., **K Thrikkadeeri** et al. (2018). *Butterflies of Christ University Main Campus---A Pictorial Guide*. Centre for Publications, Christ University, Bangalore, India. 

# Presentations

## Contributed

\begin{tabbing}

\textbf{2023}. \= Talk: \textit{Citizen Science at NCF Field Sites}. Presented with Mittal Gala. \\
\> NCF Annual Meet 2023, Mysuru, IN. \\

\textbf{2022}. \> Talk: \textit{The impact of the COVID-19 pandemic on birding and birds in India}. \\
\> NCF Annual Meet 2022, Mysuru, IN. \href{https://kartrick.rbind.io/talk/2022_ncf-am_covid-ebirding/}{(See slides or code)} \\

\textbf{2022}. \> Talk: \textit{The impact of the COVID-19 pandemic on birding and birds in India}. \\
\> International Ornithological Congress 2022, online. \href{https://kartrick.rbind.io/talk/2022_ioc-covid-ebirding/}{(See slides or code)} \\

\textbf{2022}. \> Poster: \textit{The impact of the COVID-19 pandemic on bird monitoring in India}. \\
\> Bird Monitoring Symposium 2022, online. \\

\textbf{2019}. \> Talk: \textit{Inventory of butterfly species along a land-use intensification gradient in moist temperate forest} \\
\> \textit{biome in Kumaon Himalayas}. \\
\> Ecology Seminar, University of South Bohemia, CZ. \\

\textbf{2018}. \> Talk: \textit{A study on avian diversity in an industrial area of the Palghat Gap}. \\
\> National Seminar on Development and Ecological Sustainability: Issues in Emerging India (DESIEI) 2018, \\
\> Bengaluru, IN. \\

\end{tabbing}
<!-- ## Public -->
# Other Experience

## Workshops

```{r}
tribble(
  ~ WHAT, ~ EVENT, ~ loc, ~ dates, ~ details,
  "Analysing eBird data with R", "Kerala Bird Monitoring Meet (KBMM) 2023", "Thrissur, IN", "Jun 2023", "Led workshop for c. 20 participants (birders) with assistance from Praveen J",

  "Introduction to Merlin and eBird tools", "Assam University, Silchar", "Silchar, IN", "May 2022", "Assisted Mittal Gala in short outdoor training session for eight MSc Physics students",
  "Introduction to Merlin and eBird tools", "Assam University, Silchar", "Silchar, IN", "May 2022", "Introduced features of Merlin Bird ID and eBird Mobile, and demonstrated practical usage",
  "Introduction to Merlin and eBird tools", "Assam University, Silchar", "Silchar, IN", "May 2022", "Interacted with students on general queries about birds and birding",
  
    "Bird monitoring and eBird", "College of Agriculture, Lembucherra", "Lembucherra, IN", "May 2022", "Assisted Mittal Gala in indoor workshop for c. 40 participants (students and local birders)",
    "Bird monitoring and eBird", "College of Agriculture, Lembucherra", "Lembucherra, IN", "May 2022", "Provided technical assistance, coordination support, and ad-hoc engagement with audience",

) %>% 
  detailed_entries(EVENT, dates, WHAT, loc, details)
```

## Field activities

```{r}
tribble(
  ~ company, ~ role, ~ loc, ~ dates, ~ details,
  "Bird Surveys", "Volunteer data collector", "IN", "2019--present", "Periyar Bird Survey (Jan 2023) in Periyar Tiger Reserve, Kerala (team lead)",
  "Bird Surveys", "Volunteer data collector", "IN", "2019--present", "Attappady Bird Survey (Dec 2022) in Attappady, Kerala (team lead)",
  "Bird Surveys", "Volunteer data collector", "IN", "2019--present", "Panna Bird Survey (Mar 2022) in Panna Tiger Reserve, Madhya Pradesh (team lead)",
  "Bird Surveys", "Volunteer data collector", "IN", "2019--present", "Wet Season Survey of Kerala Bird Atlas (Jul 2019) in Silent Valley National Park, Kerala",

      "Field research", "Team member", "Dudhwa, IN", "Apr 2023", "Contributed to data collection and discussions during the Bengal Florican survey (part of the grassland monitoring project of The Habitats Trust) in Dudhwa--Pilibhit landscape, Uttar Pradesh",
  
    "Expeditions", "Expedition member", "Betul, IN", "Feb 2023", "Joined mini-expedition to survey the birds of Betul, an underbirded district in Madhya Pradesh"
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

## Organisational

```{r}
tribble(
  ~ WHAT, ~ EVENT, ~ loc, ~ dates, ~ details,
  
  "Organiser", "North Wayanad Forest Division Bird Survey 2023", "North Wayanad, IN", "Mar 2023", "Helped formulate survey methodology, and managed technical logistics (eBird as a tool) and data quality",
  
  "Organiser, Editor", "National Seminar DESIEI 2018", "Bengaluru, IN", "Dec 2018", 
  "Member of symposium's Organising Committee",
  "Organiser, Editor", "National Seminar DESIEI 2018", "Bengaluru, IN", "Dec 2018", 
  "Led editorial work including editing, proofreading, typesetting, and publishing of Abstracts book",
) %>% 
  detailed_entries(WHAT, dates, EVENT, loc, details)
```

## Volunteering

```{r}
tribble(
  ~ WHAT, ~ EVENT, ~ loc, ~ dates, ~ details,
  "Volunteer", "Bird Monitoring Symposium", "Online", "Mar 2023", "Managed session talks, Q&As and comments on Discord, as well as assisted participants with queries",
  "Volunteer", "NCF Annual Meet", "Mysuru, IN", "Oct 2022", "MCd a session of talks",
  "Volunteer", "Bird Monitoring Symposium", "Online", "Apr 2022", "Managed session talks, Q&As and comments on Slack, as well as assisted participants with queries",
) %>% 
  detailed_entries(WHAT, dates, EVENT, loc, details)
```

# Memberships

```{r}

tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Volunteer", "Forest Watch", "Wayanad, Kerala, India", "2019--present", NA,
  "MSc Student", "Laboratory of Multitrophic Interactions", "České Budějovice, Czech Republic", "2019--2021", NA, 
  "Student Volunteer", "Green Army, Christ University", "Bangalore, Karnataka, India", "2016--19", "A student-based forum for wildlife and conservation",
    "Student Volunteer", "Green Army, Christ University", "Bangalore, Karnataka, India", "2016--19", "Organised and took part in multiple nature camps and day-treks",
    "Student Volunteer", "Green Army, Christ University", "Bangalore, Karnataka, India", "2016--19", "Helped organise national seminars and conducted several awareness programmes like wildlife-themed workshops",
    "Student Volunteer", "Green Army, Christ University", "Bangalore, Karnataka, India", "2016--19", "Conducted tree counts and tree plantation drives",
    "Student Volunteer", "Green Army, Christ University", "Bangalore, Karnataka, India", "2016--19", "Worked for the rejuvenation of a dying lake in Bangalore city which included working with government authorities and acted as a liaison for the local communities"
) %>% 
  detailed_entries(role, dates, company, loc, details)

```


# Referees

## Mgr. Katerina Sam, Ph.D.
Head, Laboratory of Multitrophic Interactions \newline
Biology Centre of Czech Republic, Ceske Budejovice, Czech Republic \newline
Email: katerinatvardikova@gmail.com \newline
Phone no.: +420 776 823 074

## Dr. Antony PU
Retired Professor, Department of Zoology \newline
CHRIST (Deemed to be University), Bangalore, Karnataka, India \newline
Email: antony.pu@christuniversity.in \newline
Phone no.: +91 9886887131, +91 8310082860