---
name: Karthik Thrikkadeeri
qualifications: MSc
position: "Senior Research Assistant"
address: "Nature Conservation Foundation, India"
profilepic: cvpic.jpg
www: kartrick.rbind.io
phone: +91 8129116328
email: "rikudoukarthik@gmail.com"
github: rikudoukarthik
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: A92330
header-includes:
  - \definecolor{linkscolor}{HTML}{66151D}
  - \hypersetup{colorlinks=true, urlcolor=linkscolor}
output: vitae::awesomecv
output_format: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(glue)
library(rorcid)
library(lubridate)
```

\hspace{1cm}
\hspace{1cm}

# Personal Information

\begin{tabbing}

\textsc{Date of Birth} \hspace{0.5cm} \= 24 March 1999 \\
\textsc{Sex} \> Male (he/him) \\
\textsc{Nationality} \> Indian \\
\textsc{Marital Status} \> Unmarried \\
\textsc{Driving Licence} \> LMV \& MCWG (India) \\
\textsc{Languages} \> English, Malayalam (native), Hindi \\
\textsc{Interests} \> Ecological research (community ecology, migration, biogeography) \\
 \> Birdwatching \href{https://ebird.org/profile/ODQxNTky}{(eBird profile)} \\
 \> Poetry and creative non-fiction writing \\
 \> Quantitative data analysis and visualisation \href{https://kartrick.rbind.io/kartrix/}{(fun data projects)} \\

\end{tabbing}

# Education

## Degrees

```{r}
orcid_educations("0000-0003-2863-5879") %>% 
  pluck("0000-0003-2863-5879", "affiliation-group", "summaries") %>% 
  bind_rows() %>% 
  # adding details to any item
  group_by(pick(everything())) %>% 
  reframe(details = case_when(
    
    `education-summary.role-title` == "MSc in Ecology" ~ c(
      "Thesis: \"Habitat selection in post-breeding temperate forest birds\"",
      "Supervisor: Kateřina Sam"
    ),
    TRUE ~ NA
    
  )) %>% 
  distinct() %>% 
  detailed_entries(what = `education-summary.role-title`,
                   when = glue("{`education-summary.start-date.year.value`}--{`education-summary.end-date.year.value`}"),
                   with = `education-summary.organization.name`,
                   where = glue("{`education-summary.organization.address.city`}, {`education-summary.organization.address.country`}"),
                   why = details)
```

## Courses/Workshops

```{r}
tribble(
  ~Name, ~Year, ~Institution, ~where, ~Details,
  "Introduction to Remote Sensing using QGIS", "21--25 Nov 2022", 
  "Azim Premji University", "Bengaluru, IN", 
  "Basic principles of remote sensing, characterising different features of land surface, generating maps with land cover statistics",
        ) %>% 
  detailed_entries(what = Name, 
                   when = Year,
                   with = Institution, 
                   where = where,
                   why = Details)
```

# Skills

## Field methods

- Point counts, line transects, all-out/opportunistic search
- Sound recording (birds), telephoto photography (birds), macro photography
- Camera trapping, PCQ vegetation sampling, radio telemetry 
- Extensive field experience in diverse and challenging landscapes, habitats and terrains
- Excellent sight and sound ID of birds (India, Europe)

## Technical

- Quantitative ecology (particularly community and macroecology) and research design
- Data curation, management, processing and wrangling
- Reproducibility and transparency in research workflows
- Editing and proofreading of written material (English)

## Software

- R, R Markdown & allies, Git/GitHub, QGIS
- ChatGPT, Bard
- Audacity, Canva, MS Office, Google Suite, ImageJ 

## Personal qualities

Patience, persistence, self-motivation, ambition, time management

# Certifications

\begin{tabbing}

2023 \hspace{0.1cm} \= \textbf{All-India Topper}: Ecology and Evolution (EY) | Graduate Aptitude Test in Engeering (GATE) 2023 \\
\> Marks: 84.33; Score: \textbf{1000} \\

2018 \hspace{0.1cm} \= \textbf{English CEFR C2}: IELTS 2018 (Academic) \\
\> Listening: 9.0; Reading: 9.0; Writing: 7.0; Speaking: 8.0; Overall Band Score: \textbf{8.5} \\

\end{tabbing}

# Work Experience

```{r}
my_emp <- orcid_employments("0000-0003-2863-5879") %>% 
  pluck("0000-0003-2863-5879", "affiliation-group", "summaries") %>% 
  bind_rows() %>% 
  mutate(across(c("employment-summary.end-date.year.value", "employment-summary.end-date.month.value"),
                ~ case_when(is.na(.) ~ "present", TRUE ~ .))) %>% 
  mutate(start_date = glue("{month(as.numeric(`employment-summary.start-date.month.value`), label = TRUE)} {`employment-summary.start-date.year.value`}"),
         end_date = case_when(
           `employment-summary.end-date.year.value` == "present" ~ `employment-summary.end-date.year.value`,
           TRUE ~ glue("{month(as.numeric(`employment-summary.end-date.month.value`), label = TRUE)} {`employment-summary.end-date.year.value`}")
         ))

detailed_emp <- tribble(
  ~`employment-summary.role-title`, ~start_date, ~details,
  
  "Senior Research Assistant", "Apr 2023", c(
    "SoIB 2023: Contributed to analysis, visualisation and writing for two chapters (large-scale trends, systematic monitoring) of report, and also produced website-specific outputs",
    "SoIB 2023: Unified various analyses into pipeline framework, and functionised/parametrised scripts and added annotations, to improve accessibility to team as well as others",
    "SoIB 2023: Cleaned, structured and organised GitHub repository to archive",
    "SoIB 2023: Contributed to editing and proofreading as well as bibliography management for the full report",
    "Created a GitHub repository to collate functions used repeatedly when working with eBird data in R---to potentially be converted into a package",
    "Created a GitHub repository to collate mapping data useful for eBird data analysis in the Indian context---mostly contains open shapefiles of administrative units"
  ),
  
  "Research Assistant", "Aug 2021", c(
    "Analysed the effect of the COVID-19 pandemic on birdwatching and eBird data in India, and its implications for research using this data; wrote up and submitted manuscript to a peer-reviewed journal",
        "Established a version control (Git/GitHub) workflow for Bird Count India analyses to enable reproducibility as well as transparency",
        "Created a periodic analysis framework to identify and track regions in India that are most underrepresented in eBird data, in order to identify regions of priority where concerted action (strategised from these metrics) is required",
        "Created eBirding point maps for the country as well as for each state in India, made easily accessible to users and updated monthly",
        "Automated several periodically occurring data analysis tasks of Bird Count India (tracking metrics, results of challenges & birding events [post-hoc from EBD and also live summaries using eBird API and R], etc.)",
        "Improved eBird data quality in India by creating updated and more fine-scale (district-wise) filters for Tripura state",
        "Assisted birders with their queries regarding eBird data and how to analyse it for their own studies"
  ),
  
  "Part-time employee", "Dec 2020", "Collated Kateřina Sam's Papua New Guinea bird datasets spanning c. 4 years and uploaded to eBird",
  
  "Part-time employee", "Oct 2020", "Calculated herbivory damage from images of collected leaves from Cameroon using ImageJ software",
  
  "Research intern", "Apr 2018", "Studied butterfly diversity patterns across a land-use intensification gradient in oak-pine forests of Kumaon Himalayas",

  "Research volunteer", "Apr 2017", c(
    "Assisted in field work and data entry for a project on breeding ecology of the Yellow-wattled Lapwing",
    "Additionally, learned basics of camera trapping, scale counting for snakes and PCQ vegetation survey"
  )
  
)

# adding details to any item
my_emp %>% 
  left_join(detailed_emp) %>% 
  distinct() %>% 
  arrange(desc(`employment-summary.start-date.year.value`),
          desc(`employment-summary.start-date.month.value`)) %>% 
  detailed_entries(what = `employment-summary.role-title`,
                   when = case_when(start_date != end_date ~ glue("{start_date}--{end_date}"),
                                    TRUE ~ start_date),
                   with = `employment-summary.organization.name`,
                   where = glue("{`employment-summary.organization.address.city`}, {`employment-summary.organization.address.country`}"),
                   why = details)

```

# Publications

## Research articles

<!-- This can be selected publications, so manually enter. Particularly since space is limited and need to highlight my name. -->

1. L Schillé, ..., **K Thrikkadeeri** et al. (2023). Latitudinal gradient in avian insectivory: complementary effects of climate, habitat and bird diversity. Preprint at *BioArxiv*: https://doi.org/10.1101/2023.01.19.524212.
1. J Praveen, ..., **K Thrikkadeeri** et al. (2022). Kerala Bird Atlas 2015---20: features, outcomes and implications of a citizen-science project. *Current Science* 122(3). 

## Reports

1. **SoIB 2023**. *State of India's Birds, 2023: Range, trends, and conservation status*. The SoIB Partnership. Pp. 119.

## Books 

1. PU Antony, ..., **K Thrikkadeeri** et al. (2018). *Butterflies of Christ University Main Campus---A Pictorial Guide*. Centre for Publications, Christ University, Bangalore, India. 

## In pipeline

1. **K Thrikkadeeri** and A Viswanathan *(rejected, in revision)*. Effects of COVID-19 pandemic on birding in India, and implications for citizen science inference.
1. **K Thrikkadeeri**, ..., A Viswanathan *(under review)*. Occurrence of West Himalayan Bush Warbler (*Locustella kashmirensis*) in Eastern Himalaya Terai.
1. **K Thrikkadeeri**, R Chanda, RD Kishore and R Singh *(under review)*. Sighting of the Jungle Cat in an urban hotspot in Bengaluru city, Karnataka, India.
1. A Viswanathan, ..., **K Thrikkadeeri** et al. *(in prep.)*. State of India’s Birds 2023: Background and Methodology.
1. **K Thrikkadeeri**, I Freiberga, LR Jorge, K Sam *(in prep.)*. Habitat selection in post-breeding temperate forest birds.
1. **K Thrikkadeeri**, ..., G Shahabuddin *(in prep.)*. A checklist of butterflies from a land-use intensification gradient in Kumaon Himalayas.

# Presentations

## Contributed

\begin{tabbing}

2023 \hspace{0.1cm} \= \textbf{Talk}: \textit{Citizen Science at NCF Field Sites}. Presented with Mittal Gala. \\
\> NCF Annual Meet 2023, Mysuru, IN. \\

2022 \hspace{0.1cm} \> \textbf{Talk}: \textit{The impact of the COVID-19 pandemic on birding and birds in India}. \\
\> NCF Annual Meet 2022, Mysuru, IN. \href{https://kartrick.rbind.io/talk/2022_ncf-am_covid-ebirding/}{(See slides or code)} \\

2022 \hspace{0.1cm} \> \textbf{Talk}: \textit{The impact of the COVID-19 pandemic on birding and birds in India}. \\
\> International Ornithological Congress 2022, online. \href{https://kartrick.rbind.io/talk/2022_ioc-covid-ebirding/}{(See slides or code)} \\

2022 \hspace{0.1cm} \> \textbf{Poster}: \textit{The impact of the COVID-19 pandemic on bird monitoring in India}. \\
\> Bird Monitoring Symposium 2022, online. \\

2019 \hspace{0.1cm} \> \textbf{Talk}: \textit{Inventory of butterfly species along a land-use intensification gradient in moist temperate forest} \\
\> \textit{biome in Kumaon Himalayas}. \\
\> Ecology Seminar, University of South Bohemia, CZ. \\

2018 \hspace{0.1cm} \> \textbf{Talk}: \textit{A study on avian diversity in an industrial area of the Palghat Gap}. \\
\> National Seminar on Development and Ecological Sustainability: Issues in Emerging India (DESIEI) 2018, \\
\> Bengaluru, IN. \\

\end{tabbing}

<!-- ## Public -->

# Workshops

```{r}
tribble(
  ~ WHAT, ~ EVENT, ~ loc, ~ dates, ~ details,
  "Analysing eBird data with R", "Kerala Bird Monitoring Meet (KBMM) 2023", "Thrissur, IN", "Jun 2023", "Led workshop for c. 20 participants (birders) with assistance from Praveen J",

  "Introduction to Merlin and eBird tools", "Assam University, Silchar", "Silchar, IN", "May 2022", "Assisted Mittal Gala in short outdoor training session for eight MSc Physics students",
  "Introduction to Merlin and eBird tools", "Assam University, Silchar", "Silchar, IN", "May 2022", "Introduced features of Merlin Bird ID and eBird Mobile, and demonstrated practical usage",
  "Introduction to Merlin and eBird tools", "Assam University, Silchar", "Silchar, IN", "May 2022", "Interacted with students on general queries about birds and birding",
  
    "Bird monitoring and eBird", "College of Agriculture, Lembucherra", "Lembucherra, IN", "May 2022", "Assisted Mittal Gala in indoor workshop for c. 40 participants (students and local birders)",
    "Bird monitoring and eBird", "College of Agriculture, Lembucherra", "Lembucherra, IN", "May 2022", "Provided technical assistance, coordination support, and ad-hoc engagement with audience",

) %>% 
  detailed_entries(EVENT, dates, WHAT, loc, details)
```

# Field Activities

```{r}
tribble(
  ~ company, ~ role, ~ loc, ~ dates, ~ details,
  "Bird Surveys", "Volunteer data collector", "IN", "2019--present", "Periyar Bird Survey (Jan 2023) in Periyar Tiger Reserve, Kerala (team lead)",
  "Bird Surveys", "Volunteer data collector", "IN", "2019--present", "Attappady Bird Survey (Dec 2022) in Attappady, Kerala (team lead)",
  "Bird Surveys", "Volunteer data collector", "IN", "2019--present", "Panna Bird Survey (Mar 2022) in Panna Tiger Reserve, Madhya Pradesh (team lead)",
  "Bird Surveys", "Volunteer data collector", "IN", "2019--present", "Wet Season Survey of Kerala Bird Atlas (Jul 2019) in Silent Valley National Park, Kerala",

      "Field research", "Team member", "Dudhwa, IN", "Apr 2023", "Contributed to data collection and discussions during the Bengal Florican survey (part of the grassland monitoring project of The Habitats Trust) in Dudhwa--Pilibhit landscape, Uttar Pradesh",
  
    "Expeditions", "Expedition member", "Betul, IN", "Feb 2023", "Joined mini-expedition to survey the birds of Betul, an underbirded district in Madhya Pradesh"
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Other Activities

## Organisational

```{r}
tribble(
  ~ WHAT, ~ EVENT, ~ loc, ~ dates, ~ details,
  
  "Organiser", "North Wayanad Forest Division Bird Survey 2023", "North Wayanad, IN", "Mar 2023", "Helped formulate survey methodology, and managed technical logistics (eBird as a tool) and data quality",
  
  "Organiser, Editor", "National Seminar DESIEI 2018", "Bengaluru, IN", "Dec 2018", 
  "Member of symposium's Organising Committee",
  "Organiser, Editor", "National Seminar DESIEI 2018", "Bengaluru, IN", "Dec 2018", 
  "Led editorial work including editing, proofreading, typesetting, and publishing of Abstracts book",
) %>% 
  detailed_entries(WHAT, dates, EVENT, loc, details)
```

## Volunteering

```{r}
tribble(
  ~ WHAT, ~ EVENT, ~ loc, ~ dates, ~ details,
  "Office Hours", "eBird data analysis consultation, Bird Count India", "Online", "Dec 2022--present", "Offered office hours consultation for individuals or groups on how to analyse eBird data (see https://birdcount.in/analysis-consultation/)",
  "Regional Reviewer & Hotspot Editor", "eBird data quality", "Online", "May 2022--present", "Regional Reviewer for Tripura, IN; Hotspot Editor for Tripura, In & Meghalaya, IN",
  "Volunteer", "Bird Monitoring Symposium", "Online", "Mar 2023", "Managed session talks, Q&As and comments on Discord, as well as assisted participants with queries",
  "Volunteer", "NCF Annual Meet", "Mysuru, IN", "Oct 2022", "MCd a session of talks",
  "Volunteer", "Bird Monitoring Symposium", "Online", "Apr 2022", "Managed session talks, Q&As and comments on Slack, as well as assisted participants with queries",
) %>% 
  detailed_entries(WHAT, dates, EVENT, loc, details)
```

## Administrative

```{r}
tribble(
  ~ WHAT, ~ EVENT, ~ loc, ~ dates, ~ details,
  "Coordinator", "High-performance server administration", "Bengaluru, IN", "2022--present", "Coordinated usage of NCF High Altitude Programme's high-end server among various interested parties, as well as its maintenance",
) %>% 
  detailed_entries(WHAT, dates, EVENT, loc, details)
```

# Mentoring

\begin{tabbing}

\textbf{Vyom Vyas} \hspace{0.2cm} \= Assisted in designing a behavioural study on the breeding ecology of Purple Sunbird \\

\end{tabbing}

\newpage

# Referees

## Dr Ashwin Viswanathan
Research Associate, Education and Public Engagement \newline
Nature Conservation Foundation, Mysuru, India \newline
Email: ashwinv@ncf-india.org \newline

## Dr Suhel Quader
Scientist, Education and Public Engagement \newline
Nature Conservation Foundation, Mysuru, India \newline
Email: suhelq@ncf-india.org \newline

## Praveen J
Scientist, Education and Public Engagement \newline
Nature Conservation Foundation, Mysuru, India \newline
Email: praveen.j@ncf-india.org \newline

## Mgr Katerina Sam, PhD
Head, Laboratory of Multitrophic Interactions \newline
Biology Centre of the Czech Academy of Sciences, České Budějovice, Czech Republic \newline
Email: katerinatvardikova@gmail.com \newline

## Dr PU Antony
Retired Professor, Department of Zoology \newline
Christ University, Bengaluru, India \newline
Email: antony.pu@christuniversity.in \newline
