---
name: Karthik Thrikkadeeri
surname: 
qualifications: BSc
position: "MSc Student"
address: "Department of Ecology, University of South Bohemia"
phone: +420 777 652 960
profilepic: cvpic.jpg
www: thepageofsixpaths.wordpress.com
email: "rikudoukarthik@gmail.com"
twitter: TrickDEerie
linkedin: 
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 3F6826
output: vitae::awesomecv
output_format: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(glue)
```

\hspace{1cm}
\hspace{1cm}

# Personal Information

\begin{tabbing}

\textsc{Date of Birth} \hspace{0.5cm} \= 24 March 1999 \\
\textsc{Sex} \> Male (he/him) \\
\textsc{Nationality} \> Indian \\
\textsc{Marital Status} \> Unmarried \\
\textsc{Driving Licence} \> LMV \& MCWG (India) \\
\textsc{Languages} \> \textit{Fluent:} \hspace{0.3cm} \= English (8.5 IELTS 2018), Malayalam (native) \\
                    \> \textit{Medium:} \> Hindi \\
                    \> \textit{Passive:} \> Kannada, Japanese

\end{tabbing}

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~Details, 
  "MSc in Ecology", "2019 -- present", "University of South Bohemia", "Ceske Budejovice, Czech Republic", "Thesis: \"Post-breeding movement of forest birds along a habitat quality gradient\"",   "MSc in Ecology", "2019 -- present", "University of South Bohemia", "Ceske Budejovice, Czech Republic", "Supervisor: Katerina Sam",
  "BSc in Biotechnology, Chemistry, Zoology", "2016 -- 19", "CHRIST (Deemed to be University)", "Bangalore, Karnataka, India", NA,
) %>% 
  detailed_entries(Degree, Year, Institution, Where, Details)
```


# Skills

\begin{tabbing}

\textsc{Software} \hspace{1cm} \= \textit{Intermediate:} \hspace{0.1cm} \= Microsoft Office, R, ImageJ, Adobe Illustrator, Adobe Lightroom \\
                          \> \textit{Beginner:} \> R Markdown, CANOCO \\
\textsc{Laboratory} \> Basic knowledge of DNA extraction, PCR, microbial culture \\
\textsc{Identification} \> Experience with birds, butterflies, odonates 

\end{tabbing}




# Working Experience

```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Part-time employee", "Biology Centre, Czech Academy of Sciences", "Ceske Budejovice, Czech Republic", "December 2020 -- present", "Collation of Katerina Sam's Papua New Guinea bird datasets spanning ca. 4 years and uploading to eBird",
  "Part-time employee", "Biology Centre, Czech Academy of Sciences", "Ceske Budejovice, Czech Republic", "October 2020", "Calculated herbivory damage from images of collected leaves from Cameroon using ImageJ software",
  "Fieldwork volunteer", "Kerala Bird Atlas---Wet Season Survey 2019", "Palakkad, Kerala, India", "July 2019", "Assisted in monsoon bird survey in Silent Valley National Park",
  "Research intern", "Centre for Ecology Development and Research (CEDAR Himalaya)", "Kumaon, Uttarakhand, India", "April 2018 -- May 2018", "Conducted a preliminary study of butterfly diversity patterns across a land-use intensification gradient in oak-pine forests of Kumaon Himalayas",
  "Research intern", "Centre for Ecology Development and Research (CEDAR Himalaya)", "Kumaon, Uttarakhand, India", "April 2018 -- May 2018", "Obtained photographic records of butterfly species without collection of specimens",
  "Research volunteer", "Agumbe Rainforest Research Station (ARRS)", "Agumbe, Karnataka, India", "April 2017 -- May 2017", "Assisted in field work and data entry for a project on the breeding ecology of the Yellow-wattled Lapwing",
  "Research volunteer", "Agumbe Rainforest Research Station (ARRS)", "Agumbe, Karnataka, India", "April 2017 -- May 2017", "Additionally, learned basics of camera trapping, scale counting for snakes and PCQ vegetation survey"
) %>% 
  detailed_entries(company, dates, role, loc, details)
```


# Presentations

## Conference Talks

\textbf{2019.} Inventory of butterfly species along a land-use intensification gradient in moist temperate forest biome in Kumaon Himalayas.
\textit{Ecology Seminar, University of South Bohemia, Czech Republic.} 

\textbf{2018.} A study on avian diversity in an industrial area of the Palghat Gap.
\textit{National Seminar on Development and Ecological Sustainability: Issues in Emerging India (DESIEI---2018), CHRIST (Deemed to be University), Bengaluru, India.}

# Publications

## Books 

1. PU Antony, ..., **K Thrikkadeeri** et al. (2018). Butterflies of Christ University Main Campus---A Pictorial Guide. *Centre for Publications, Christ University, Bangalore, India*. 

## Literary

1. **TD Eerie** (under review). Romance Dawn: Five Poems. *Vayavya*.

# Memberships

```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "MSc Student", "Laboratory of Multitrophic Interactions", "Ceske Budejovice, Czech Republic", "2019 -- present", NA, 
  "Student Volunteer", "Forest Watch", "Wayanad, Kerala, India", "2019 -- present", NA,
  "Editorial Board", "Organising Committee, National Seminar DESIEI---2018", "Bangalore, Karnataka, India", "2018", "Majorly involved in all editorial work including editing, proofreading, typesetting and publishing of Abstracts book",
  "Student Volunteer", "Green Army", "Bangalore, Karnataka, India", "2016 -- 19", "A student-based forum for wildlife and conservation",
    "Student Volunteer", "Green Army", "Bangalore, Karnataka, India", "2016 -- 19", "Organised and took part in multiple nature camps and day-treks",
    "Student Volunteer", "Green Army", "Bangalore, Karnataka, India", "2016 -- 19", "Helped organise national seminars and conducted several awareness programmes like wildlife-themed workshops",
    "Student Volunteer", "Green Army", "Bangalore, Karnataka, India", "2016 -- 19", "Conducted tree counts and tree plantation drives",
    "Student Volunteer", "Green Army", "Bangalore, Karnataka, India", "2016 -- 19", "Worked for the rejuvenation of a dying lake in Bangalore city which included working with government authorities and acted as a liaison for the local communities"
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Referees

## Mgr. Katerina Sam, Ph.D.
Head, Laboratory of Multitrophic Interactions \newline
Biology Centre of Czech Republic, Ceske Budejovice, Czech Republic \newline
Email: katerinatvardikova@gmail.com \newline
Phone no.: +420 776 823 074

## Dr. Antony PU
Retired Professor, Department of Zoology \newline
CHRIST (Deemed to be University), Bangalore, Karnataka, India \newline
Email: antony.pu@christuniversity.in \newline
Phone no.: +91 9886887131, +91 8310082860