---
name: Karthik Thrikkadeeri
surname: 
qualifications: BSc
position: "MSc Student"
address: "Department of Ecology, University of South Bohemia"
phone: +420 777 652 960
profilepic: cvpic.jpg
www: thepageofsixpaths.wordpress.com
email: "rikudoukarthik@gmail.com"
twitter: 
linkedin: thrikkadeeri
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 3F6826
output: vitae::awesomecv
output_format: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(glue)
```

\hspace{1cm}
\hspace{1cm}

# Personal Information

\begin{tabbing}

\textbf{Date of Birth:} \hspace{1.7cm} \= 24 March 1999 \\
\textbf{Sex:} \> Male  (he/him) \\
\textbf{Nationality:} \> Indian \\
\textbf{Marital Status:} \> Unmarried \\
\textbf{Driving Licence:} \> LMV \& MCWG (India) \\
\textbf{Languages:} \> \textbf{Malayalam} \hspace{2cm} \= \textbf{English} \hspace{2cm} \= \textbf{Hindi} \hspace{2cm} \= \textbf{Kannada} \\
                    \> Fluent (native speaker) \> Proficient \> Intermediate \> Passive \\
                    \> \> 8.5 IELTS---2018 

\end{tabbing}



\hspace{1cm}

# Skills

\begin{tabbing}

\textbf{Software skills:} \hspace{1cm} \= Microsoft Office, Adobe Lightroom, Adobe Illustrator (Intermediate)\\
                          \> R, CANOCO, R Markdown (Beginner) \\
\textbf{Identification skills:} \> Experience with birds, butterflies, odonates \\
\textbf{Laboratory skills:} \> Basic knowledge of DNA extraction, PCR, microbial culture

\end{tabbing}


\hspace{1cm}

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~Details, 
  "MSc in Ecology", "2019 -- present", "University of South Bohemia", "Ceske Budejovice, Czech Republic", "Thesis: \"Post-breeding movement of forest birds along a habitat quality gradient\"",   "MSc in Ecology", "2019 -- present", "University of South Bohemia", "Ceske Budejovice, Czech Republic", "Supervisor: Mgr., Ph.D. Katerina Sam",
  "BSc in Biotechnology, Chemistry, Zoology", "2016 -- 19", "CHRIST (Deemed to be University)", "Bangalore, Karnataka, India", NA,
  "Senior Secondary Education", "2014 -- 16", "Palghat Lions School", "Palakkad, Kerala, India", NA,
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where, Details)
```


\hspace{1cm}

# Research Experience

```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Field work volunteer", "Kerala Bird Atlas---Wet Season Survey 2019", "Palakkad, Kerala, India", "July 2019", "Assisted in monsoon bird survey in Silent Valley National Park",
  "Research Intern", "Centre for Ecology Development and Research (CEDAR Himalaya)", "Kumaon, Uttarakhand, India", "April 2018 -- May 2018", "Conducted a preliminary study of butterfly diversity patterns across a land-use intensification gradient in oak-pine forests of Kumaon Himalayas",
  "Research Intern", "Centre for Ecology Development and Research (CEDAR Himalaya)", "Kumaon, Uttarakhand, India", "April 2018 -- May 2018", "Obtained photographic records of butterfly species without collection of specimens",
  "Research Volunteer", "Agumbe Rainforest Research Station (ARRS)", "Agumbe, Karnataka, India", "April 2017 -- May 2017", "Assisted in field work and data entry for a project on the breeding ecology of the Yellow-wattled Lapwing",
  "Research Volunteer", "Agumbe Rainforest Research Station (ARRS)", "Agumbe, Karnataka, India", "April 2017 -- May 2017", "Additionally, learned basics of camera trapping, scale counting for snakes and PCQ vegetation survey"
) %>% 
  detailed_entries(company, dates, role, loc, details)
```


\hspace{1cm}

# Presentations

## Research Talks
```{r}
tribble(
  ~ when, ~ title, ~ event, ~ where, 
  "2019", "Inventory of Butterfly Species along a Land-use Intensification Gradient in Moist Temperate Forest Biome in Kumaon Himalayas", "Student Talk, Ecology Seminar", "University of South Bohemia, Ceske Budejovice, Czech Republic",
  "2018", "A Study on Avian Diversity in an Industrial Area of the Palghat Gap", "Student Talk, National Seminar---DESIEI-2018", "CHRIST (Deemed to be University), Bengaluru, India", 
  
) %>% 
  arrange(desc(when)) %>%
  detailed_entries(
    what = glue("<event> \\newline <where>", .open = "<", .close = ">"),
    when = when,
    with = title,
    where = ,
    why = , 
    .protect = FALSE
    )
```



\hspace{1cm}

# Publications

## Books 
```{r}
tibble(
    title = "Butterflies of Christ University Main Campus - A Pictorial Guide",
    author = "PU Antony, ..., K Thrikkadeeri, et al.",
    journal = "",
    number = " ",
    cites = 0,
    year = "2018",
    cid = NA,
    pubid = NA
    ) %>% 
  detailed_entries(
    what = author,
    when = year,
    with = title,
    ) 
```
## Abstracts
```{r}
  tibble(
    title = "A Study on Avian Diversity in an Industrial Area of the Palghat Gap",
    author = "K Thrikkadeeri, PU Antony",
    journal = "DESIEI-2018",
    number = " ",
    cites = 0,
    year = "2018",
    cid = NA,
    pubid = NA
  ) %>% 
  arrange(desc(year)) %>%
  detailed_entries(
    what = author,
    when = year,
    with = title,
    where = journal
  )
```



\hspace{1cm}

# Memberships

```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Student Volunteer", "Forest Watch", "Wayanad, Kerala, India", "2019 -- present", "A charitable organisation aiming to combine the passion of youth with knowledge of wildlife biology and human society, to design locally apt conservation strategies",
  "Editorial Board", "Organising Committee---National Seminar on Development and Ecological Sustainability: Issues in Emerging India (DESIEI-2018)", "Bangalore, Karnataka, India", "2018", "Majorly involved in all editorial work including editing, proofreading, typesetting and publishing of the Abstracts book",
  "Student Volunteer", "Green Army, CHRIST (Deemed to be University)", "Bangalore, Karnataka, India", "2016 -- 19", "A student-based forum for wildlife and conservation",
    "Student Volunteer", "Green Army, CHRIST (Deemed to be University)", "Bangalore, Karnataka, India", "2016 -- 19", "Organised and took part in multiple nature camps and day-treks",
    "Student Volunteer", "Green Army, CHRIST (Deemed to be University)", "Bangalore, Karnataka, India", "2016 -- 19", "Helped organise national seminars and conducted several awareness programmes like wildlife-themed workshops",
    "Student Volunteer", "Green Army, CHRIST (Deemed to be University)", "Bangalore, Karnataka, India", "2016 -- 19", "Conducted tree counts and tree plantation drives",
    "Student Volunteer", "Green Army, CHRIST (Deemed to be University)", "Bangalore, Karnataka, India", "2016 -- 19", "Worked for the rejuvenation of a dying lake in Bangalore city which included working with government authorities and acted as a liaison for the local communities"
) %>% 
  detailed_entries(role, dates, company, loc, details)
```


\hspace{1cm}

# Referees

## Mgr. Katerina Sam, Ph.D.
Head, Laboratory of Multitrophic Interactions \newline
Biology Centre of Czech Republic, Ceske Budejovice, Czech Republic \newline
Email: katerinatvardikova@gmail.com \newline
Phone no.: +420 776 823 074

## Dr. Antony PU
Professor, Department of Zoology \newline
CHRIST (Deemed to be University), Bangalore, Karnataka, India \newline
Email: antony.pu@christuniversity.in \newline
Phone no.: +91 9886887131, +91 8310082860